---
title: "An Employment Predictor Application"
subtitle: "A Shiny Application and Reproducible Pitch"
author: "Ian Dobbs"
date: "`r Sys.Date()`"
output: 
        ioslides_presentation:
                widescreen: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, options(scipen=999))
```

## Application Data & Purpose

Longley's Economic Regression Data

- A macroeconomic data set which provides a well-known example for a highly collinear regression.
- A data frame with 7 economic variables, observed yearly from 1947 to 1962

Purpose of application

- A simple and easy to use linear regression model to predict the number of employed for a given population size

## Application Description

- A slider to select a given population size
- A check box to show or hide the regression model
- Real time plot update as population size changes
- A 'Result' tab to display results in the form of a scatter plot, and text output
- A 'Documentation' tab to provide basic instructions on app usage
- URL to shiny application https://iandobbs.shinyapps.io/longley/
- URL to server.R and ui.R code on github https://github.com/IanDobbs/DDPproject/tree/gh-pages/longley

## The Regression Model

- The regression model `lm(Employed ~ Population, longley)` produces the following coefficients and r-squared values to determine if the explanatory model is a good fit.

```{r model}
model <- lm(Employed ~ Population, longley)
summary(model)$coef
summary(model)$r.squared
```

- The coefficients indicate that population increases employment (as expected). The low p-value >0.05 and high r.squared value indicate a strong relationship for the explanatory model.

## Residual Plot

- The residual plots do not show any unexpected patterns which is further evidence that the model is a strong predictor.

```{r residuals}
par(mfrow = c(2, 2))
plot(model)
```

